Reproduction

### 2024-09-03 pages/reproduction.qmd
docs(reproduction): make study descriptions more consistent (e.g. mentioning model language and packages each time)

<!-- TODO: Modify descriptions so each contains consistent information about each study - e.g. making sure each includes a mention of what was used to make model (e.g. R simmer, base R, python simpy) -->

**@shoaib_simulation_2021:** This is a discrete-event simulation modelling primary health centres (PHCs) in India. There are four patient types: outpatients, inpatients, childbirth cases and antenatal care patients. Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines. The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources. *(Article published as @shoaib_simulation_2022, but we used the green open access pre-print).* <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@huang_optimizing_2019:** This is a discrete-event simulation model of an endovascular clot retrieval (ECR) service. ECR is a treatment for acute ischaemic stroke. The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway. The model is created using R Simmer. The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR). A few scenarios are tried to help examine why the wait times are so high for the angioINR. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@lim_staff_2020:** This is a discrete-event simulation modelling the transmission of COVID-19 in laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). The model is created using Python. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@kim_modelling_2021:** This study adapts a previously developed discrete-event simulation model for abdominal aortic aneurysm (AAA) screening of men in England. It aims to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM is a discrete-event simulation modelling intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

>>>>

**@shoaib_simulation_2021:** Uses **python (salabim)** to model primary health centres (PHCs) in India. The model has four patient types: outpatients, inpatients, childbirth cases and antenatal care patients. Four model configurations are developed based on observed PHC practices or government-mandated operational guidelines. The paper explores different operational patterns for scenarios where very high utilisation was observed, to explore what might help reduce utilisation of these resources. Note: The article was as @shoaib_simulation_2022, but we used the green open access pre-print @shoaib_simulation_2021. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@huang_optimizing_2019:** Uses **R (simmer)** to model an endovascular clot retrieval (ECR) service. ECR is a treatment for acute ischaemic stroke. The model includes the stroke pathway, as well as three other pathways that share resources with the stroke pathway: an elective non-stroke interventional neuroradiology pathway, an emergency interventional radiology pathway, and an elective interventional radiology pathway. The paper explores waiting times and resource utilisation - particularly focussing on the biplane angiographic suite (angioINR). A few scenarios are tried to help examine why the wait times are so high for the angioINR. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@lim_staff_2020:** Uses **python (numpy and pandas)** to model the transmission of COVID-19 in a laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@kim_modelling_2021:** Adapts a previously developed **R (Rcpp, expm, msm, foreach, iterators, doParallel)** model for abdominal aortic aneurysm (AAA) screening of men in England. The model is adapted/used to explore different approaches to resuming screening and surgical repair for AAA, as these survives were paused or substantially reduced during COVID-19 due to concerns about virus transmission. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM uses **Python (simpy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>
